---
title: "Create Dataset"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)

library(tidytext)
library(SnowballC)
library(tidyverse)
library(rjson)
```

```{r, read_data}
#' read a csv table from the data directory
#'
#' read a csv table from the data directory when given a text string in the file name
#'
#' @param path: A text string contained in the file name that uniquely identifies that desired file.
read_data <- function(path) {  
  dir_list <- list.dirs(file.path('data'))
  index    <- dir_list %>% str_detect(path)  
  data     <- dir_list[index]  
  files    <- list.files(data)    
  index    <- files %>% str_detect(regex(str_c(path,'.*','\\.csv'),ignore_case = TRUE)  ) 
  d_pc     <- read_csv(file.path(data,files[index]))
  d_pc
}

```

```{r, augment_names}
#' Add a tag to the end of a data table name
#' 
#' Add a tag to the end of a data table name to uniquely identify it.
#'
#' @param file_name: The file name to change 
#' @param tag: A text string to add to the end of a file name.
augment_names <- function(file_name,tag){ 
  d <- read_rds(file.path('data',str_c(file_name,'.rds')))
  d <- d %>% select(COUNTY, everything())   
  names(d) <- c("COUNTY",str_c(names(d)[2:length(d)],tag))
  d
}

```

This data set contains information on cost and event counts.

* Postbirthing
* Prebirthing
* Prescription Cost
* Total Claims
* Total Cost
* Total Prescriptions

Each item contains information on

* Diabetes
* Diagnosis of obesity
* Diagnosis of stress
* Diagnosis of substance abuse
* Emergency Room
* Maternal Health
* 


## Prescription Related Claims by Recipient County
```{r}
parse_names <-function(d) {
  text_df <- tibble(text = stringr::str_split(names(d),pattern = '_')) %>% 
    unnest %>% 
    distinct  %>% 
    unnest_tokens(word,text) %>% 
    anti_join(stop_words, by = 'word') %>% 
    mutate(word = wordStem(word)) %>% 
    distinct
    
  #text_df %>%  unnest_tokens(word, text)
}
```


```{r,create_indicators}

create_indicators <- function(d) {
 d %>% 
  gather(value = "value", key = "type", -COUNTY)    %>% 
  mutate(features = str_split(type, pattern = '_'))       %>% 
  unnest(features)       %>% 
  mutate(features = tolower(features)) %>% 
  mutate(features = wordStem((features))) %>% 
  mutate(i = 1) %>% 
  spread(value = 'i', key = 'features') 
}
#d2 %>% create_indicators()
```


```{r}
names(d2)
```


data set
:  rx_claims
```{r}
h2 <- 'https://hub.mph.in.gov/dataset/b8192d38-cbbc-438e-a3c5-fe7be0b3e010/resource/0cf62b0a-4526-40a4-a632-08cdd9840ae9/download/03_prescription_related_claims_by_recipient_county.csv'
h3 <- 'https://hub.mph.in.gov/dataset/b6c042b5-ff33-4b4f-a7b1-85cdbcdd0c64/resource/0f7cb803-0237-4191-bddc-259a5a51ff25/download/24_prescription_related_claims_of_mothers_with_an_er_visit_by_recipient_county.csv'
h4 <- 'https://hub.mph.in.gov/dataset/beeb019d-9bfc-4e41-bc15-aa27165a51dc/resource/95f202d9-7abd-4691-8625-a1895e21f3b4/download/23_claims_of_mothers_with_an_er_visit_by_recipient_county.csv'
h5 <- 'https://hub.mph.in.gov/dataset/c5e2b9d8-ab44-490e-9e37-eee3e9db3b62/resource/4ef71011-5784-4ab9-b2d0-63ba2a8b4f10/download/22_mothers_with_an_er_visit_by_recipient_county.csv'

control <- tribble(
  ~https, ~tag,
  h2    , 'Prescription Related Claims',
  h3    , 'Prescription Related Claims of Mothers with an ER Visit' ,
  h4    , 'Claims of Mothers With and ER Visit',
  h5    , 'Mothers With and ER Visit'
)

read_and_merge <- function(https, tag) {
  d <- read_csv(https) %>%  
    create_indicators %>% 
    mutate(tag = tag) %>% 
    select(-type)
}

control %>% pmap(read_and_merge) %>% 
  bind_rows
  
```

```{r, eval=FALSE}


d2 <- read_csv('https://hub.mph.in.gov/dataset/b8192d38-cbbc-438e-a3c5-fe7be0b3e010/resource/0cf62b0a-4526-40a4-a632-08cdd9840ae9/download/03_prescription_related_claims_by_recipient_county.csv')

write_rds(d2,file.path('data','d2.rds'))
```

```{r}
d2
```

```{r}
d2 %>% create_indicators
```

```{r}
d2 <- read_rds(file.path('data','d2.rds'))
d2 <- augment_names('d2',"_rx_claims")
d2 %>% head
```
## Prescription Related Claims of Mothers with an ER Visit by Recipient County

data set
:  rx_claims_er

```{r, eval=FALSE}
d3 <- read_csv('https://hub.mph.in.gov/dataset/b6c042b5-ff33-4b4f-a7b1-85cdbcdd0c64/resource/0f7cb803-0237-4191-bddc-259a5a51ff25/download/24_prescription_related_claims_of_mothers_with_an_er_visit_by_recipient_county.csv')

write_rds(d3,file.path('data','d3.rds'))
```
```{r}
d3
```

```{r}
d3 %>% create_indicators
```

```{r}
d3 <- read_rds(file.path('data','d3.rds'))
d3 <- augment_names('d3',"_rx_claims_er")
glimpse(d3)
```

## Claims of Mothers with an ER Visit by Recipient County 

data set
:  er

```{r, eval=FALSE}
d4 <- read_csv('https://hub.mph.in.gov/dataset/beeb019d-9bfc-4e41-bc15-aa27165a51dc/resource/95f202d9-7abd-4691-8625-a1895e21f3b4/download/23_claims_of_mothers_with_an_er_visit_by_recipient_county.csv')

write_rds(d4,file.path('data','d4.rds'))
d4
```

```{r}
d4 <- read_rds(file.path('data','d4.rds'))
d4 <- augment_names('d4','_er')
d4 %>% head
```

## Mothers with an ER Visit by Recipient County 

data set
:  er

```{r,eval=FALSE}
d5 <- read_csv('https://hub.mph.in.gov/dataset/c5e2b9d8-ab44-490e-9e37-eee3e9db3b62/resource/4ef71011-5784-4ab9-b2d0-63ba2a8b4f10/download/22_mothers_with_an_er_visit_by_recipient_county.csv')
write_rds(d5,file.path('data','d5.rds'))
```

```{r}
d5 <- read_rds(file.path('data','d5.rds'))
d5 <- augment_names('d5','_er' )
head(d5)
```


## Prescription Related Claims of Mothers Diagnosed with stress by Recipient County 

data set
:  rx_stress

```{r, eval=FALSE}
d6 <- read_csv('https://hub.mph.in.gov/dataset/1a0db5ce-8736-4642-abcd-3a7b2c411dca/resource/89e3c9f4-115f-428f-9191-c8bd21ccd8b5/download/21_prescription_related_claims_of_mothers_diagnosed_with_stress_by_recipient_county.csv')

write_rds(d6,file.path('data','d6.rds'))
d6
```

```{r}
d6 <- read_rds(file.path('data','d6.rds'))
d6 <- augment_names('d6','_rx_stress' )
head(d6)
```
## Claims of Mothers Diagnosed with Stress by Recipient County

data set
:  dx_stress

```{r,eval=FALSE}
d7<- read_csv('https://hub.mph.in.gov/dataset/9de3f203-8ea0-4b44-8909-0b911e8593b1/resource/6a4e21ee-6ebd-45de-bb82-45950983d3b7/download/20_claims_of_mothers_diagnosed_with_stress_by_recipient_county.csv')

write_rds(d7,file.path('data','d7.rds'))
```
```{r}
d7 <- read_rds(file.path('data','d7.rds'))
d7 <- augment_names('d7','_dx_stress' )
head(d7)
```

## Mothers with a Stress Related Claim by Recipient County 

data set
:  stress_claim

```{r, eval=FALSE}
d8 <- read_csv('https://hub.mph.in.gov/dataset/96a26efa-d9b9-4131-81e2-2f0804d069c3/resource/1a677106-5ef8-49c0-b918-b6905b8a4e0b/download/19_mothers_with_a_stress_related_claim_by_recipient_county.csv')

write_rds(d8,file.path('data','d8.rds'))
```
`
```{r}
d8 <- read_rds(file.path('data','d8.rds'))
d8 <- augment_names('d8','_stress' )
head(d8)
```

## Prescription Related Claims of Mothers with Pre-Term Delivery by Recipient County

data set
:  rx_pre_term

```{r, eval=FALSE}
d9 <- read_csv('https://hub.mph.in.gov/dataset/07146ade-a340-47f3-9839-ef01c619dc62/resource/a6e70e65-e868-4023-a166-9dab80352d3c/download/18_prescription_related_claims_of_mothers_with_preterm_delivery_by_recipient_county.csv')

write_rds(d9,file.path('data','d9.rds'))
```


```{r}
d9 <- read_rds(file.path('data','d9.rds'))
d9 <- augment_names('d9','_rx_pre_term' )
head(d8)
```


## Claims of Mothers with Pre-Term Delivery by Recipient County 

data
:  claims_pre_term

```{r, eval=FALSE}
d13 <- read_csv('https://hub.mph.in.gov/dataset/d450e6c5-9877-4840-9e97-b2b96cb1c08e/resource/b8951968-b4ea-4559-a409-6380fdf8ff5d/download/17_claims_of_mothers_with_preterm_delivery_by_recipient_county.csv')
write_rds(d13,file.path('data','d13.rds'))
```

```{r}
d13 <- read_rds(file.path('data','d13.rds'))
d13 <- augment_names('d13','_pre_term' )
head(d13)
```

## Prescription Related Claims of Mothers with Substance Use by Recipient County 

data
:  rx_substance

```{r, eval=FALSE}
d14 <- read_csv('https://hub.mph.in.gov/dataset/b3ed9eaa-cb54-44ef-bf83-0fb272999e2b/resource/2f636563-172a-4efc-98c0-15bd45be3610/download/15_prescription_related_claims_of_mothers_with_substance_use_by_recipient_county.csv')

write_rds(d14,file.path('data','d14.rds'))
```


```{r}
d14 <- read_rds(file.path('data','d14.rds'))
d14 <- augment_names('d14','_dx_substance' )
head(d14)
```

## Claims of Mothers with Substance Use by Recipient County 

data
: substance
```{r, eval=FALSE}
d15 <- read_csv('https://hub.mph.in.gov/dataset/9d6ec92d-de6c-445d-ae9a-e242af1a9661/resource/84d1532c-ced4-4c1c-b892-ee6722c127b7/download/14_claims_of_mothers_with_substance_use_by_recipient_county.csv')

write_rds(d15,file.path('data','d15.rds'))
```

```{r}
d15 <- read_rds(file.path('data','d15.rds'))
d15 <- augment_names('d15','_substance' )
head(d15)
```

## Prescription Related Claims of Mothers Diagnosed with Obesity by Recipient County 

data
:  rx_obesity

```{r, eval=FALSE}
d16 <- read_csv('https://hub.mph.in.gov/dataset/b1906fbd-aafb-4a4f-9f35-fbeefc92a07b/resource/0f46cd23-530f-4358-ae39-b74603797926/download/09_prescription_related_claims_of_mothers_diagnosed_with_obesity_by_recipient_county.csv')

write_rds(d16,file.path('data','d16.rds'))
```

```{r}
d16 <- read_rds(file.path('data','d16.rds'))
d16 <- augment_names('d16','_obesity' )
head(d16)
```

## Birth Count by Recipient County

data
: birth_count
```{r, eval=FALSE}
d17 <- read_csv('https://hub.mph.in.gov/dataset/55e2cbf7-085d-4086-84dd-79613d06aa23/resource/59faf526-d40f-432f-83e9-fc4bfe3179fc/download/04_birth_count_by_recipient_county.csv')

write_rds(d17,file.path('data','d17.rds'))
```
```{r}
d17 <- read_rds(file.path('data','d17.rds'))
d17 <- augment_names('d17','_birth_count' )
head(d17)
```

## Maternal Health Claims by Recipient County

data
:  maternal_health

```{r, eval=FALSE}
d18 <- read_csv('https://hub.mph.in.gov/dataset/ae880b2f-e119-499a-8c82-5238d04c7001/resource/05f64b98-4451-490a-aa64-a4cd0638f59c/download/02_maternal_health_claims_by_recipient_county.csv')

write_rds(d18,file.path('data','d18.rds'))
```
```{r}
d18 <- read_rds(file.path('data','d18.rds'))
d18 <- augment_names('d18','_maternal_health' )
head(d18)
```

## Mothers with a Substance Use Related Claim by Recipient County 

data
: substance_use

```{r, eval=FALSE}
d19 <- read_csv('https://hub.mph.in.gov/dataset/e21c8eb9-23fa-43f7-8c32-fcb98ab2d39a/resource/c5ee0772-96f4-4e15-93f2-03bb79aa0bcd/download/13_mothers_with_a_substance_use_related_claim_by_recipient_county.csv')

write_rds(d19,file.path('data','d19.rds'))
```

```{r}
d19 <- read_rds(file.path('data','d19.rds'))
d19 <- augment_names('d19','_substance_use' )
head(d19)
```

## Prescription Related Claims of Mothers with Diabetes by Recipient County 

data
: rx diabetes

```{r, eval=FALSE}
d20 <- read_csv('https://hub.mph.in.gov/dataset/9ba31ad1-3876-4291-9260-a4aa670de16c/resource/ee28629b-afe0-4463-9513-712958474c07/download/12_prescription_related_claims_of_mothers_with_diabetes_by_recipient_county.csv')

write_rds(d20,file.path('data','d20.rds'))
```

```{r}
d20 <- read_rds(file.path('data','d20.rds'))
d20 <- augment_names('d20','_rx_diabetes' )
head(d20)
```

## Claims of Mothers with Diabetes by Recipient County

data
: diabetes

```{r, eval=FALSE}
d21 <- read_csv('https://hub.mph.in.gov/dataset/a5acf50e-7bfb-4a26-b3cc-e55213075eb8/resource/0b9de5bf-258a-4942-ae95-30fe333d7582/download/11_claims_of_mothers_with_diabetes_by_recipient_county.csv')

write_rds(d21,file.path('data','d21.rds'))
```

```{r}
d21 <- read_rds(file.path('data','d21.rds'))
d21 <- augment_names('d21','_diabetes' )
head(d21)
```

## Mothers with a Diabetes Related Claim by Recipient County

data
: count diabetes 
```{r, eval=FALSE}
d22 <- read_csv('https://hub.mph.in.gov/dataset/6d202617-09b4-4303-b110-5a7ee18bdc45/resource/1817e997-badb-4d9a-b457-a2c067798744/download/10_mothers_with_a_diabetes_related_claim_by_recipient_county.csv')

write_rds(d22,file.path('data','d22.rds'))
```

```{r}
d22 <- read_rds(file.path('data','d22.rds'))
d22 <- augment_names('d22','_diabetes' )
head(d22)
```

## Claims of Mothers Diagnosed with Obesity by Recipient County 

data 
:  dx obesity
```{r, eval=FALSE}
d23 <- read_csv('https://hub.mph.in.gov/dataset/1850d68e-a8ce-4408-9f3e-0ee4f0acde04/resource/2299013f-dd4c-47a3-b9ec-ebf0c05e1d3e/download/08_claims_of_mothers_diagnosed_with_obesity_by_recipient_county.csv')

write_rds(d23,file.path('data','d23.rds'))
```

```{r}
d23 <- read_rds(file.path('data','d23.rds'))
d23 <- augment_names('d23','_dx_obesity' )
head(d23)
```

## Count of Mothers Diagnosed with Obesity by Recipient County 

data
:  count obesity

```{r, eval=FALSE}
d24 <- read_csv('https://hub.mph.in.gov/dataset/baa800c2-c6ba-45f5-a1bf-11e9326c28e5/resource/867296c1-54cf-41cc-824b-31524ec1e7ab/download/07_count_of_mothers_diagnosed_with_obesity_by_recipient_county.csv')

write_rds(d24,file.path('data','d24.rds'))
```
```{r}
d24 <- read_rds(file.path('data','d24.rds'))
d24 <- augment_names('d24','_obesity' )
head(d24)
```

## Infant Prescription Related Claims by Recipient County 

data
:  rx_infant

```{r, eval=FALSE}
d25 <- read_csv('https://hub.mph.in.gov/dataset/490755a6-4755-4060-ab26-646c544636ed/resource/c0994219-e833-4337-95e3-8edab622ca95/download/06_infant_prescription_related_claims_by_recipient_county.csv')

write_rds(d25,file.path('data','d25.rds'))
```

```{r}
d25 <- read_rds(file.path('data','d25.rds'))
d25 <- augment_names('d25','_rx_infant' )
head(d25)
```

## Infant Claims by Recipient County

data
:  infant
```{r, eval=FALSE}
d26 <- read_csv('https://hub.mph.in.gov/dataset/d72a6291-8b56-4a5b-bc1c-bfdfd71b6dd1/resource/209bf480-bae2-4518-ba0d-244f21c825eb/download/05_infant_claims_by_recipient_county.csv')

write_rds(d26,file.path('data','d26.rds'))
```

```{r}
d26 <- read_rds(file.path('data','d26.rds'))
d26 <- augment_names('d26','_infant' )
head(d26)
```

## Count of Mothers by Recipient County 

data
:  Mothers count
```{r, eval=FALSE}
d27 <- read_csv('https://hub.mph.in.gov/dataset/74881778-735c-4260-9a62-f8afe4cd46a0/resource/9b18a616-681c-4844-ab80-1ab46dd3dff0/download/01_count_of_mothers_by_recipient_county.csv')

write_rds(d27,file.path('data','d27.rds'))
d27
```

```{r}
d27 <- read_rds(file.path('data','d27.rds'))
d27 <- augment_names('d27','_mothers' )
head(d27)
```


```{r,include=TRUE}
n <- c(2:9,13:27)
n
d <- str_c('d',n)  %>% map(get) %>% purrr::reduce(function(x,y){x %>% left_join(y, by = 'COUNTY')})
d <- d %>% select(sort(names(d)))
glimpse(d)
```
```{r}

write_csv(d,file.path('data','d.csv'))
```




























