---
title: "R Notebook"
output: html_notebook
---

## Mothers Diagnosed with Intrauterine Growth Restriction (IURG), or Pre-Eclampsia by ZipCode 

data set
:  1

```{r,eval=FALSE}
d1 <- read_csv('https://hub.mph.in.gov/dataset/dcdcee0c-ca93-4586-af9c-c843046ffc92/resource/6776c647-2d76-44e1-93fe-02b4ee739dde/download/regenstrief_dataset_momandbaby_datapalooza.csv', col_types = 'iiddddd')
write_rds(d1,file.path('data','d1.rds'))
```

```{r, include=TRUE}
d1 <- read_rds(file.path('data','d1.rds'))
d1
```
This data gives the zip code.

Map the zip to fips, then fips to county.


First get and fips to city

A data set with fips and county
```{r}
fips_zip <- read_csv('https://query.data.world/s/uwauhovv3qj4wv22csxxrdblltbcsj')  
```
The `fips_zip` data.
```{r, include=TRUE}
fips_zip %>% head
```


```{r}
fips_county <- read_csv('https://query.data.world/s/x6dprlo6izfwfty7qaagn6phhdgsu3') %>% 
  mutate(STATEFP = as.integer(STATEFP)) %>% 
  mutate(COUNTYFP =  as.integer(COUNTYFP))
```
The `fips_country` data.

```{r, include=TRUE}
fips_county %>% head
```


```{r}
city <- maps::county.fips %>% filter(str_detect(polyname,'indiana'))   %>% 
  mutate(city = str_match(polyname,'^(.*),(.*)')[,3]) %>% 
  select(-polyname) %>% 
  mutate(STATEFP = floor(fips/1000)) %>% 
  mutate(COUNTYFP = fips %% 1000)
```

The `city` data.
```{r, include=TRUE}
city %>% head
```
Combine the `fips_zip` data, the `fips_country` data, and the `city` data.
```{r, include=TRUE}
zip_level <-fips_zip  %>% 
  mutate(STATEFP = as.integer(STATE)) %>% 
  mutate(COUNTYFP = as.integer(COUNTY)) %>% 
  select(-STATE,-COUNTY) %>% 
  mutate(zip_code = str_sub(as.character(ZCTA5),1,4)) %>% 
  mutate(zip_code = as.integer(zip_code)) %>% 
  inner_join(fips_county, by = c('STATEFP','COUNTYFP')) %>% 
  filter(STATE == 'IN') %>% 
  inner_join(city, by = c('STATEFP','COUNTYFP')) %>% 
  select(STATEFP, COUNTYFP, STATE,city,zip_code, COUNTYNAME, everything())   
zip_level

```
The resulting edited version.
```{r, include=TRUE}
zip_3_county <- zip_level %>% 
  mutate(zip_code = floor(zip_code/10))  %>% 
  select(zip_code, everything()) %>% 
  distinct(STATEFP, COUNTYFP, STATE, zip_code, COUNTYNAME)  %>% 
  arrange(COUNTYNAME)
zip_3_county
```

Add the county to the d1 dataset.
```{r}
d1_county <- d1 %>% 
  inner_join(zip_3_county, by = 'zip_code') %>% 
  filter(COUNTYNAME == 'Marion County') %>% 
  arrange(year, zip_code)
```

```{r, include=TRUE}
d1_county %>% head
```


Write the d1_country to the data set d1_country.csv.
```{r, echo=TRUE, include=TRUE}
write_csv(d1_county, file.path('data','d1_county.csv'))
```

```{r}
data("stop_words")
library(SnowballC)
```
